### 2010-09-20 doc/manuals/chelonia/arc-storage-manual.tex
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/

pidfile=/tmp/chelonia1.pid
logfile=/var/log/chelonia1.log
debug=ERROR

@@

pidfile=/tmp/chelonia2.pid
logfile=/var/log/chelonia2.log
debug=ERROR

@@

pidfile=/tmp/chelonia3.pid
logfile=/var/log/chelonia3.log
debug=ERROR

>>>>

pidfile=/tmp/chelonia1.pid
logfile=/var/log/arc/chelonia1.log
debug=ERROR

@@

pidfile=/tmp/chelonia2.pid
logfile=/var/log/arc/chelonia2.log
debug=ERROR

@@

pidfile=/tmp/chelonia3.pid
logfile=/var/log/arc/chelonia3.log
debug=ERROR

### 2010-09-20 doc/manuals/configuration/configuration_manual.tex
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/

Logging options should be specified under the \texttt{Logger} element under the
\texttt{Server} element. The \texttt{File} element specifies which file to write
log messages to and if not present log messages will be written to the
\texttt{/var/log/arched.log} file. Each log message is associated with a log
level which indicates the serverity of the message. The following log levels
exist in WS-ARC, ordered by serverity: \texttt{FATAL}, \texttt{ERROR},
\texttt{WARNING}, \texttt{INFO}, \texttt{VERBOSE} and \texttt{DEBUG}. With
the \texttt{Level} element the level of messages being reported can be
specified. Log messages with a higher or same level as specified by the
\texttt{Level} element will be written to the log file. The default log level is
\texttt{WARNING}.

@@

\subsection{Examples}\label{sec:XML examples}
\subsubsection{Echo Service}
\begin{lstlisting}[language=xml]
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
               xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
               xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
               xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
               xmlns:echo="http://www.nordugrid.org/schemas/echo/2009/08"
               xmlns:infosys="http://www.nordugrid.org/schemas/infosys/2009/08">
  <cfg:Server>
    <cfg:PidFile>/tmp/arched.pid</cfg:PidFile>
    <cfg:Logger>
      <cfg:File>/var/log/arched.log</cfg:File>
      <cfg:Level>WARNING</cfg:Level>
    </cfg:Logger>
  </cfg:Server>
  <ModuleManager>
    <Path>/usr/lib/arc</Path>
  </ModuleManager>
  <Plugins>
    <Name>mcctls</Name>
    <Name>mcchttp</Name>
    <Name>mccsoap</Name>
    <Name>mcctcp</Name>
  </Plugins>
  <Chain>
    <Component name="tcp.service" id="tcp">
      <next id="http"/>
      <tcp:Listen>
        <tcp:Interface>0.0.0.0</tcp:Interface>
        <tcp:Version>4</tcp:Version>
      </tcp:Listen>
    </Component>
    <Component name="http.service" id="http">
      <next id="soap">POST</next>
      <next id="plexer">GET</next>
    </Component>
    <Component name="soap.service" id="soap">
      <next id="plexer"/>
    </Component>
    <Plexer id="plexer">
      <next id="echo">/Echo</next>
    </Plexer>
    <Service name="echo" id="echo">
      <echo:prefix>[</echo:prefix>
      <echo:suffix>]</echo:suffix>
    </Service>
  </Chain>
</cfg:ArcConfig>
\end{lstlisting}

@@

Two XML attributes have been introduced to be able to create a mapping, and
these are \texttt{inisections} and \texttt{initag}. XML elements which should be
configurable in INI format must specify these attributes. The \texttt{initag}
attribute defines the name of the tag which represent the respective XML element
in the INI configuration file, and the \texttt{inisections} attribute is used to
specify, as a space separated list, which sections the tag can occur in. The
list is ordered, in the sense that the listed sections is searched, in the
specified order, for the tag specified by the \texttt{initag} attribute, and if
found in a section no further sections will be searched. Only leaf XML elements
(elements with no child elements) should be mapped, mapping non leaf element
result in a undefined behaviour. A profile example of a XML element mapping is
shown in the listing below:
\begin{lstlisting}[language=xml,title=ElementMapping.xml]
...
<Server>
  ...
  <Logger>
    <File inisections="special common"
          initag="logfile">/var/log/arched.log</File>
    ...
  </Logger>
</Server>
...
\end{lstlisting}
And this example profile can then be utilised in a INI configuration file as:
\begin{lstlisting}[language=xml,title=ElementMapping.ini]
profile=ElementMapping.xml
logfile=/etc/arc/arched.log
...
[ special ]
logfile=/var/arc/arched.log
...
\end{lstlisting}
And the resulting XML configuration will look like:
\begin{lstlisting}[language=xml]
...
<Server>
  ...
  <Logger>
    <File>/var/arc/arched.log</File>
    ...
  </Logger>
</Server>
...
\end{lstlisting}

@@

\begin{center}
\small
\begin{tabular}{>{\ttfamily}l>{\ttfamily}l>{\ttfamily}l}
\toprule
\textrm{\textbf{XML element/attribute}} & \textrm{\textbf{INI tag}} & \textrm{\textbf{Default value}}\\
\midrule
/Server/PidFile & pidfile & /var/run/arched.pid\\
/Server/User & user & \textrm{None} \\
/Server/Group & group & \textrm{None} \\
/Server/Logger/File & logfile & /var/log/arched.log \\
/Server/Logger/Level & loglevel & WARNING \\
/Server/Logger/Maxsize & logmaxsize & \textrm{None} \\
/Server/Logger/Backups & logbackups & \textrm{None} \\
/ModuleManager/Path & libpath & \textrm{None} \\
/Plexer/next & endpointpattern & \textrm{None} \\
\midrule
\multicolumn{3}{c}{\textbf{TCP MCC}}\\
\midrule
/Component/Listen/Interface & interface & 0.0.0.0 \\
/Component/Listen/Port & port & 60000\\
/Component/Listen/Version & ipversion & \textrm{None} \\
/Component/Listen/NoDelay & nodelay & false\\
/Component/Listen/Timeout & timeout & \textrm{None}\\
/Component/Limit & limit & \textrm{None}\\
/Component/Limit.drop & drop & \textrm{None}\\
\midrule
\multicolumn{3}{c}{\textbf{TLS MCC}}\\
\midrule
/Component/KeyPath & x509\_host\_key & /etc/grid-security/hostkey.pem\\
/Component/CertificatePath & x509\_host\_cert & /etc/grid-security/hostcert.pem\\
/Component/CACertificatePath & x509\_cacert\_path & \textrm{None}\\
/Component/CACertificatesDir & x509\_cacert\_dir & /etc/grid-security/certificates\\
%/Component/CACertificatesDir.PolicyGlobus & policyglobus \\
/Component/ClientAuthn & clientauthn & true\\
%/Component/VOMSCertTrustDNChain/VOMSCertTrustDN &  \\
%/Component/VOMSCertTrustDNChain/VOMSCertTrustRegex &  \\
%Component/VOMSCertTrustDNChainsLocation & \\
/Component/Handshake & handshake & TLS\\
\bottomrule
\end{tabular}
\end{center}

>>>>

Logging options should be specified under the \texttt{Logger} element under the
\texttt{Server} element. The \texttt{File} element specifies which file to write
log messages to and if not present log messages will be written to the
\texttt{/var/log/arc/arched.log} file. Each log message is associated with a log
level which indicates the serverity of the message. The following log levels
exist in WS-ARC, ordered by serverity: \texttt{FATAL}, \texttt{ERROR},
\texttt{WARNING}, \texttt{INFO}, \texttt{VERBOSE} and \texttt{DEBUG}. With
the \texttt{Level} element the level of messages being reported can be
specified. Log messages with a higher or same level as specified by the
\texttt{Level} element will be written to the log file. The default log level is
\texttt{WARNING}.

@@

\subsection{Examples}\label{sec:XML examples}
\subsubsection{Echo Service}
\begin{lstlisting}[language=xml]
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
               xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
               xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
               xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
               xmlns:echo="http://www.nordugrid.org/schemas/echo/2009/08"
               xmlns:infosys="http://www.nordugrid.org/schemas/infosys/2009/08">
  <cfg:Server>
    <cfg:PidFile>/tmp/arched.pid</cfg:PidFile>
    <cfg:Logger>
      <cfg:File>/var/log/arc/arched.log</cfg:File>
      <cfg:Level>WARNING</cfg:Level>
    </cfg:Logger>
  </cfg:Server>
  <ModuleManager>
    <Path>/usr/lib/arc</Path>
  </ModuleManager>
  <Plugins>
    <Name>mcctls</Name>
    <Name>mcchttp</Name>
    <Name>mccsoap</Name>
    <Name>mcctcp</Name>
  </Plugins>
  <Chain>
    <Component name="tcp.service" id="tcp">
      <next id="http"/>
      <tcp:Listen>
        <tcp:Interface>0.0.0.0</tcp:Interface>
        <tcp:Version>4</tcp:Version>
      </tcp:Listen>
    </Component>
    <Component name="http.service" id="http">
      <next id="soap">POST</next>
      <next id="plexer">GET</next>
    </Component>
    <Component name="soap.service" id="soap">
      <next id="plexer"/>
    </Component>
    <Plexer id="plexer">
      <next id="echo">/Echo</next>
    </Plexer>
    <Service name="echo" id="echo">
      <echo:prefix>[</echo:prefix>
      <echo:suffix>]</echo:suffix>
    </Service>
  </Chain>
</cfg:ArcConfig>
\end{lstlisting}

@@

Two XML attributes have been introduced to be able to create a mapping, and
these are \texttt{inisections} and \texttt{initag}. XML elements which should be
configurable in INI format must specify these attributes. The \texttt{initag}
attribute defines the name of the tag which represent the respective XML element
in the INI configuration file, and the \texttt{inisections} attribute is used to
specify, as a space separated list, which sections the tag can occur in. The
list is ordered, in the sense that the listed sections is searched, in the
specified order, for the tag specified by the \texttt{initag} attribute, and if
found in a section no further sections will be searched. Only leaf XML elements
(elements with no child elements) should be mapped, mapping non leaf element
result in a undefined behaviour. A profile example of a XML element mapping is
shown in the listing below:
\begin{lstlisting}[language=xml,title=ElementMapping.xml]
...
<Server>
  ...
  <Logger>
    <File inisections="special common"
          initag="logfile">/var/log/arc/arched.log</File>
    ...
  </Logger>
</Server>
...
\end{lstlisting}
And this example profile can then be utilised in a INI configuration file as:
\begin{lstlisting}[language=xml,title=ElementMapping.ini]
profile=ElementMapping.xml
logfile=/etc/arc/arched.log
...
[ special ]
logfile=/var/arc/arched.log
...
\end{lstlisting}
And the resulting XML configuration will look like:
\begin{lstlisting}[language=xml]
...
<Server>
  ...
  <Logger>
    <File>/var/arc/arched.log</File>
    ...
  </Logger>
</Server>
...
\end{lstlisting}

@@

\begin{center}
\small
\begin{tabular}{>{\ttfamily}l>{\ttfamily}l>{\ttfamily}l}
\toprule
\textrm{\textbf{XML element/attribute}} & \textrm{\textbf{INI tag}} & \textrm{\textbf{Default value}}\\
\midrule
/Server/PidFile & pidfile & /var/run/arched.pid\\
/Server/User & user & \textrm{None} \\
/Server/Group & group & \textrm{None} \\
/Server/Logger/File & logfile & /var/log/arc/arched.log \\
/Server/Logger/Level & loglevel & WARNING \\
/Server/Logger/Maxsize & logmaxsize & \textrm{None} \\
/Server/Logger/Backups & logbackups & \textrm{None} \\
/ModuleManager/Path & libpath & \textrm{None} \\
/Plexer/next & endpointpattern & \textrm{None} \\
\midrule
\multicolumn{3}{c}{\textbf{TCP MCC}}\\
\midrule
/Component/Listen/Interface & interface & 0.0.0.0 \\
/Component/Listen/Port & port & 60000\\
/Component/Listen/Version & ipversion & \textrm{None} \\
/Component/Listen/NoDelay & nodelay & false\\
/Component/Listen/Timeout & timeout & \textrm{None}\\
/Component/Limit & limit & \textrm{None}\\
/Component/Limit.drop & drop & \textrm{None}\\
\midrule
\multicolumn{3}{c}{\textbf{TLS MCC}}\\
\midrule
/Component/KeyPath & x509\_host\_key & /etc/grid-security/hostkey.pem\\
/Component/CertificatePath & x509\_host\_cert & /etc/grid-security/hostcert.pem\\
/Component/CACertificatePath & x509\_cacert\_path & \textrm{None}\\
/Component/CACertificatesDir & x509\_cacert\_dir & /etc/grid-security/certificates\\
%/Component/CACertificatesDir.PolicyGlobus & policyglobus \\
/Component/ClientAuthn & clientauthn & true\\
%/Component/VOMSCertTrustDNChain/VOMSCertTrustDN &  \\
%/Component/VOMSCertTrustDNChain/VOMSCertTrustRegex &  \\
%Component/VOMSCertTrustDNChainsLocation & \\
/Component/Handshake & handshake & TLS\\
\bottomrule
\end{tabular}
\end{center}

### 2010-09-20 doc/manuals/echo/echo-manual.tex
Switching documents to bibliography style which is supposed to be present in latex distributions. Fixes in some documents and build procedures.
Move ARC to using Logrotate instead of built-in log rotation Move ARC logging default from /var/log to /var/log/arc/

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Zsombor Nagy},
  pdftitle = {The Echo service},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\begin{verbatim}
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
	xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
	xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
	xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
	xmlns:echo="http://www.nordugrid.org/schemas/echo/2009/08">
    <cfg:Server>
        <cfg:PidFile>tmp/arched.pid</cfg:PidFile>
        <cfg:Logger>
            <cfg:File>/var/log/arched.log</cfg:File>
            <cfg:Level>ERROR</cfg:Level>
        </cfg:Logger>
    </cfg:Server>
    <ModuleManager>
        <Path inisections="common" initag="libpath">/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins>
        <Name>mcctls</Name>
        <Name>mcchttp</Name>
        <Name>mccsoap</Name>
        <Name>mcctcp</Name>
    </Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/>
            <tcp:Listen>
               <tcp:Interface>0.0.0.0</tcp:Interface>
               <tcp:Port>50000</tcp:Port>
               <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
            <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
            <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
            <next id="plexer">GET</next>
            <next id="plexer">PUT</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="echo">^/Echo$</next>
        </Plexer>
        <Service name="echo" id="echo">
            <echo:prefix>[</echo:prefix>
            <echo:suffix>]</echo:suffix>
        </Service>
    </Chain>
</cfg:ArcConfig>
\end{verbatim}
% section configuration (end)

@@

\begin{verbatim}
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
	xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
	xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
	xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
	xmlns:echo="http://www.nordugrid.org/schemas/echo/2009/08"
	xmlns:py="http://www.nordugrid.org/schemas/pythonwrapper/2009/08">
    <cfg:Server>
        <cfg:PidFile>tmp/arched.pid</cfg:PidFile>
        <cfg:Logger>
            <cfg:File>/var/log/arched.log</cfg:File>
            <cfg:Level>ERROR</cfg:Level>
        </cfg:Logger>
    </cfg:Server>
    <ModuleManager>
        <Path inisections="common" initag="libpath">/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins>
        <Name>mcctls</Name>
        <Name>mcchttp</Name>
        <Name>mccsoap</Name>
        <Name>mcctcp</Name>
    </Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/>
            <tcp:Listen>
               <tcp:Interface>0.0.0.0</tcp:Interface>
               <tcp:Port>50000</tcp:Port>
               <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
            <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
            <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
            <next id="plexer">GET</next>
            <next id="plexer">PUT</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="echo">^/Echo$</next>
        </Plexer>
        <Service name="pythonservice" id="echo">
            <py:ClassName>echo_python.EchoService.EchoService</py:ClassName>
            <echo:prefix>[</echo:prefix>
            <echo:suffix>]</echo:suffix>
        </Service>
    </Chain>
</cfg:ArcConfig>
\end{verbatim}
% section configuration_of_the_python_echo_service (end)

>>>>

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Zsombor Nagy},
  pdftitle = {The Echo service},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\begin{verbatim}
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
	xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
	xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
	xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
	xmlns:echo="http://www.nordugrid.org/schemas/echo/2009/08">
    <cfg:Server>
        <cfg:PidFile>tmp/arched.pid</cfg:PidFile>
        <cfg:Logger>
            <cfg:File>/var/log/arc/arched.log</cfg:File>
            <cfg:Level>ERROR</cfg:Level>
        </cfg:Logger>
    </cfg:Server>
    <ModuleManager>
        <Path inisections="common" initag="libpath">/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins>
        <Name>mcctls</Name>
        <Name>mcchttp</Name>
        <Name>mccsoap</Name>
        <Name>mcctcp</Name>
    </Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/>
            <tcp:Listen>
               <tcp:Interface>0.0.0.0</tcp:Interface>
               <tcp:Port>50000</tcp:Port>
               <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
            <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
            <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
            <next id="plexer">GET</next>
            <next id="plexer">PUT</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="echo">^/Echo$</next>
        </Plexer>
        <Service name="echo" id="echo">
            <echo:prefix>[</echo:prefix>
            <echo:suffix>]</echo:suffix>
        </Service>
    </Chain>
</cfg:ArcConfig>
\end{verbatim}
% section configuration (end)

@@

\begin{verbatim}
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
	xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
	xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
	xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
	xmlns:echo="http://www.nordugrid.org/schemas/echo/2009/08"
	xmlns:py="http://www.nordugrid.org/schemas/pythonwrapper/2009/08">
    <cfg:Server>
        <cfg:PidFile>tmp/arched.pid</cfg:PidFile>
        <cfg:Logger>
            <cfg:File>/var/log/arc/arched.log</cfg:File>
            <cfg:Level>ERROR</cfg:Level>
        </cfg:Logger>
    </cfg:Server>
    <ModuleManager>
        <Path inisections="common" initag="libpath">/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins>
        <Name>mcctls</Name>
        <Name>mcchttp</Name>
        <Name>mccsoap</Name>
        <Name>mcctcp</Name>
    </Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/>
            <tcp:Listen>
               <tcp:Interface>0.0.0.0</tcp:Interface>
               <tcp:Port>50000</tcp:Port>
               <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
            <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
            <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
            <next id="plexer">GET</next>
            <next id="plexer">PUT</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="echo">^/Echo$</next>
        </Plexer>
        <Service name="pythonservice" id="echo">
            <py:ClassName>echo_python.EchoService.EchoService</py:ClassName>
            <echo:prefix>[</echo:prefix>
            <echo:suffix>]</echo:suffix>
        </Service>
    </Chain>
</cfg:ArcConfig>
\end{verbatim}
% section configuration_of_the_python_echo_service (end)
